The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-08 paper/mri paper.tex
more on paper

We conduct a formal multiscale analysis. Our perturbations are characterized in terms of fast and slow-moving variables, in order to simultaneously track their evolution on fast and slow scales. The relative scalings of the fast and slow scales are determined as follows. When our four equations are linearized for perturbations of the form $e^{\sigma t + i k_x x + i k_z z}$, we can derive the linear dispersion relation, which is fourth order in $\sigma$. The fast and slow variables are then defined such that each of the temporal and spatial eigenvalues appear at the same lowest order in the linear dispersion relation. The scalings are:

@@

Note that these are the same scalings as apply to Rayleigh-B\'enard convection and hydrodynamic Taylor Couette flow.

>>>>

We conduct a formal multiscale analysis. Our perturbations are characterized in terms of fast and slow-moving variables, in order to simultaneously track their evolution on fast and slow scales. The relative scalings of the fast and slow scales are determined as follows. When our four equations are linearized for axisymmetric perturbations of the form $e^{\sigma t + i k_x x + i k_z z}$, we can derive the linear dispersion relation, which is fourth order in $\sigma$. The fast and slow variables are then defined such that each of the temporal and spatial eigenvalues appear at the same lowest order in the linear dispersion relation. The scalings are:

@@

Note that these are the same scalings as apply to Rayleigh-B\'enard convection and hydrodynamic Taylor Couette flow. Each operator is expanded to reflect these scalings -- for instance, $\partial_z$ becomes $\partial_z + \epsilon\partial_Z$.

The state vector is expanded in orders of $\epsilon$:

\beq
\mathbf{V} = \epsilon\mathbf{V_1} + \epsilon^2\mathbf{V_2} + \epsilon^3\mathbf{V_3} + ...
\eeq
